PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.

### 2024-03-08 docs/_tex/index.tex
first part of Laurent's comments

\usepackage{fontspec}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\newlength\Oldarrayrulewidth
\newlength\Oldtabcolsep
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{float}
\usepackage{wrapfig}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\usepackage{bookmark}

@@

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{ccccc}

@@

\tabularnewline

\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Country}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Site}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Name}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Altitude}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Utility}}} \\

\ascline{1.5pt}{000000}{1-5}\endfirsthead

\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Country}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Site}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Name}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Altitude}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Utility}}} \\

\ascline{1.5pt}{000000}{1-5}\endhead

\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Arz\ Island}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{12m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Training}}} \\

\ascline{1.5pt}{BEBEBE}{3-5}

\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Duer}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{12m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Training}}} \\

\ascline{1.5pt}{BEBEBE}{3-5}

\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{\multirow[c]{-3}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Gulf\ of\ Morbihan}}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Duer}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\

\ascline{1.5pt}{666666}{2-5}

\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Barbâtre}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\

\ascline{1.5pt}{BEBEBE}{3-5}

\multicolumn{1}{>{}c}{\multirow[c]{-5}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{France}}}}} & \multicolumn{1}{>{}c}{\multirow[c]{-2}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Bourgneuf\ Bay}}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{L'Epine}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\

\ascline{1.5pt}{000000}{1-5}

\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Inner\ Lagoon}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\

\ascline{1.5pt}{BEBEBE}{3-5}

\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Mataducos}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\

\ascline{1.5pt}{BEBEBE}{3-5}

\multicolumn{1}{>{}c}{} & \multicolumn{1}{>{}c}{} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Gafanha}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{120m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation}}} \\

\ascline{1.5pt}{BEBEBE}{3-5}

\multicolumn{1}{>{}c}{\multirow[c]{-4}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Portugal}}}}} & \multicolumn{1}{>{}c}{\multirow[c]{-4}{*}{\parbox{0.75in}{\centering \textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Aveiro\ Lagoon}}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 1.5pt}>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Gafanha}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{12m}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Training}}} \\

\ascline{1.5pt}{000000}{1-5}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

@@

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{ccc}

@@

\tabularnewline

\ascline{1.5pt}{666666}{1-3}

\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Class}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Training\ Pixels}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation\ Pixels}}} \\

\ascline{1.5pt}{666666}{1-3}\endfirsthead

\ascline{1.5pt}{666666}{1-3}

\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Class}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Training\ Pixels}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Validation\ Pixels}}} \\

\ascline{1.5pt}{666666}{1-3}\endhead

\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Bacillariophyceae}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{4,475}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{3,371,920}}} \\

\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Chlorophyceae}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{17,140}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{6,258,737}}} \\

\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Magnoliopsida}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{221,065}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{69,079,189}}} \\

\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Phaeophyceae}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{169,936}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{18,481,141}}} \\

\multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{Rhodophyceae}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{5,771}}} & \multicolumn{1}{>{}c}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{3,515,421}}} \\

\ascline{1.5pt}{666666}{1-3}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

>>>>

\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\usepackage{bookmark}

@@

\begin{table}

@@

\includegraphics[width=6.63in,height=\textheight]{Figures/table_flights.png}

\end{table}%

@@

\begin{table}

@@

\includegraphics[width=6.63in,height=\textheight]{Figures/table_validation_px.png}

\end{table}%

### 2024-03-08 index.qmd
first part of Laurent's comments

@@

flextable(df)  %>%
  merge_v(j = 1) %>%
  merge_v(j = 2) %>%
    border_remove() %>%
    hline_top(border=brdr1) %>%
    hline(i=5, border=brdr1) %>%
    hline(i=1,j = 3:5, border=brdr2) %>%
    hline(i=2, border=brdr2) %>%
    hline(i=3, j = 2:5, border=brdr3) %>%
    hline(i=4, j = 3:5, border=brdr2) %>%
    hline(i=6, border=brdr2) %>%
    hline(i=6, j = 1:2, border=brdr1) %>%
    hline(i=7, border=brdr2) %>%
    hline(i=8, border=brdr2) %>%
    hline(i=9, border=brdr1) %>%
    vline(j=2, border = brdr1) %>%
    flextable::align(align = "center",part = "all") %>%
    flextable::align(align = "center",part = "header") %>%
  # set_caption(caption = "Table 1 List of drone Flight, summarising the date, the altitude and the purpose of each flight.") %>%
  set_table_properties(layout = "autofit")

@@

@@

df_training %>% 
  left_join(df_validation, by = "True") %>% 
  rename(`Validation Pixels` = "n",
         Class = "True",
         `Training Pixels` = "Training_Pixels") %>% 
  flextable() %>% 
  # border_remove() %>%
  flextable::align(align = "center",part = "all") %>%
  flextable::align(align = "center",part = "header") %>% 
  set_table_properties(layout = "autofit")

>>>>

```{r Table1 building}
#| cache: false
#| echo: false
#| eval: false
#| warning: false

@@

 i = 16.5 # width of the side borders in the word_document output (in centimeters)
 w = i*0.3937 # width of the side borders in the word_document output (in inches)

flx1<-flextable(df)  %>%
  flextable::width(width = (w/(ncol(df)))) %>% 
  merge_v(j = 1) %>%
  merge_v(j = 2) %>%
    border_remove() %>%
    hline_top(border=brdr1) %>%
    hline(i=5, border=brdr1) %>%
    hline(i=1,j = 3:5, border=brdr2) %>%
    hline(i=2, border=brdr2) %>%
    hline(i=3, j = 2:5, border=brdr3) %>%
    hline(i=4, j = 3:5, border=brdr2) %>%
    hline(i=6, border=brdr2) %>%
    hline(i=6, j = 1:2, border=brdr1) %>%
    hline(i=7, border=brdr2) %>%
    hline(i=8, border=brdr2) %>%
    hline(i=9, border=brdr1) %>%
    vline(j=2, border = brdr1) %>%
    flextable::align(align = "center",part = "all") %>%
    flextable::align(align = "center",part = "header") %>%
  # set_caption(caption = "Table 1 List of drone Flight, summarising the date, the altitude and the purpose of each flight.") %>%
  set_table_properties(layout = "autofit")

save_as_image(flx1, "Figures/table_flights.png", res = 300)
```

knitr::include_graphics("Figures/table_flights.png")
```

@@

```{r Table2 building}
#| cache: false
#| echo: false
#| eval: false
#| warning: false

 i = 16.5 # width of the side borders in the word_document output (in centimeters)
 w = i*0.3937 # width of the side borders in the word_document output (in inches)

df_flx2<-df_training %>% 
  left_join(df_validation, by = "True") %>% 
  rename(`Validation Pixels` = "n",
         Class = "True",
         `Training Pixels` = "Training_Pixels")
flx2 <- df_flx2 %>% 
  flextable() %>% 
  flextable::width(width = (w/(ncol(df_flx2)))) %>% 
  # border_remove() %>%
  flextable::align(align = "center",part = "all") %>%
  flextable::align(align = "center",part = "header") %>% 
  set_table_properties(layout = "autofit")

save_as_image(flx2, "Figures/table_validation_px.png", res = 300)

@@

knitr::include_graphics("Figures/table_validation_px.png")
```
